Verifying Demonstrations

### 2018-03-21 paper/protocol.tex
Removes ref to DBPK eqn, adds SPK explicitly

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\gets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \mleftright
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(pid = g_T^{1/(k+cid)}\) as \(pid^k = g_T g_T^{-cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{DBPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T pid^{-cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(wid\gets \ACprf[_{sk_W}][pid] = 
  g_T^{1/(k_W+pid)}\) (as above) and in the same way \(wsig\gets 
  \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]\).
Then the witness returns \((wid, t_s', l, wsig)\) to the participant.
Now both the participant and the witness have the tuple \(\pi = (pid, wid, t_s, 
  t_s', l, wsig)\) which constitutes a proof share of the participant 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
    wsig]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
correctness of \(pid\).
More specifically,
\begin{multline*}
  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
    \begin{aligned}
      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
    \end{aligned} \\
      (cid, pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the participant uploads the tuple \[
  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
\] for permanent storage.

>>>>

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\gets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}\label{eq:DBPK}
  \DBPK\left\{(k, r, r') :
    v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \quad \land \right. \\
      \left. pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(pid = g_T^{1/(k+cid)}\) as \(pid^k = g_T g_T^{-cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{DBPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T pid^{-cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(
  wid\gets \ACprf[_{sk_W}][pid] = g_T^{1/(k_W+pid)}
\) (as above) and in the same way \(
  wsig\gets \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]
\).
Then the witness returns \(
  (wid, t_s', l, wsig)
\) to the participant.
Now both the participant and the witness have the tuple \(
  \pi = (pid, wid, t_s, t_s', l, wsig)
\) which constitutes a proof share of the participant (\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
    wsig]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
correctness of \(pid\), \ie we simply use the Fiat-Shamir heuristic to turn the 
\ac{DBPK} above into \iac{NIZK} proof.
More specifically,
\begin{multline*}
  \pi_{pid}\gets \SPK\left\{(k, r, r') : \phantom{g_T^{1/(k+cid)}}\right. \\
      v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
      pid = \left. g_T^{1/(k+cid)} \right\} \\
        (cid, pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the participant uploads the tuple \[
  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
\] for permanent storage.
